### 2018-10-30 pilot_manuscript.Rmd
updated analyses

```{r new_data, include = FALSE}
##open the Warriner data for later
warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum

@@

```{r update-mlm, include = FALSE}

#harm_final_data clean up
harm_final_data$percent = harm_final_data$Freq / harm_final_data$wordcount *100
harm_final_data$lean = factor(harm_final_data$Source, 
                              levels = names(table(harm_final_data$Source)),
                              labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
harm_final_data$lean = gsub("1", "", harm_final_data$lean)

harm_final_data$weighted = harm_final_data$percent*harm_final_data$valence

>>>>

```{r new_data, include = FALSE}
##open the Warriner data for later
warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)

@@

```{r update-mlm, include = FALSE}
#harm_final_data clean up
#multiply by frequency and create percentage
harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100

#flatten down to sum by article 
harm_final_temp = aggregate(harm_final_data$weight, 
          by = list(harm_final_data$URL),
          FUN = sum, na.rm = T)
colnames(harm_final_temp) = c("URL", "MFDweight")

harm_final_temp$lean[grepl("nytimes.com", harm_final_temp$URL) |
                       grepl("npr.org", harm_final_temp$URL)] = "Liberal"
harm_final_temp$lean[grepl("breitbart.com", harm_final_temp$URL) |
                       grepl("foxnews.com", harm_final_temp$URL)] = "Conservative"

harm_final_temp$Source[grepl("nytimes.com", harm_final_temp$URL)] = "NY Times"
harm_final_temp$Source[grepl("npr.org", harm_final_temp$URL)] = "NPR"
harm_final_temp$Source[grepl("foxnews.com", harm_final_temp$URL)] = "Fox"
harm_final_temp$Source[grepl("breitbart.com", harm_final_temp$URL)] = "Breitbart"

harm_model = lme(MFDweight ~ lean, 
                 data = harm_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
